### 2017-11-12 manuscript.rmd
updated pdf

	knitr::opts_chunk$set( 
	  echo = FALSE,
	  message=FALSE, 
	  warning=FALSE,
    dev="png", 
    # dev.args=list( compression="lzw" ), # for tiff
    dpi=600,
    cache=TRUE
  )

@@

The KMRR study [@KryuchkovaMostacci:2016iw] followed excellent practices in reproducibility. They posted all data and code needed to re-execute their analyses at figshare: https://figshare.com/articles/Tissue-specificity_of_gene_expression_diverges_slowly_between_orthologs_and_rapidly_between_paralogs/3493010/2 . We slightly altered their `Rscript.R` to simplify file paths and specify one missing variable. This modified script and their data files are available in the github repository for this paper, as are the intermediate files that were generated by their analysis script that we used in our own analyses. We\ obtained the `Compara.75.protein.nh.emf` gene trees [@Herrero:2016jj] from ftp://ftp.ensembl.org/pub/release-75/emf/ensembl-compara/homologies/ and include them in our github repository. These gene trees include branch lengths, annotate each internal node as being a duplication or speciation event, and provide a clade label for each internal node.

@@

	g_k_density = 
		ggplot(D, aes(x,y)) + 
			geom_line() + 
			geom_polygon( data = shade, aes(x, y) ) +
			xlab("K") +
			ylab("density") +
			theme_classic() +
			geom_vline(xintercept = thresh, col="grey") +
			geom_text(aes(x=thresh, label=thresh_label, y=mean(range(y))), colour="grey", angle=90) +
			ggtitle( "A Density of K" )

>>>>

	knitr::opts_chunk$set( 
	  echo=FALSE,
	  message=FALSE, 
	  warning=FALSE,
    dev="png", 
    # dev.args=list( compression="lzw" ), # for tiff
    dpi=600,
    cache=TRUE
  )

@@

The KMRR study [@KryuchkovaMostacci:2016iw] followed excellent practices in reproducibility. They posted all data and code needed to re-execute their analyses at figshare: https://figshare.com/articles/Tissue-specificity_of_gene_expression_diverges_slowly_between_orthologs_and_rapidly_between_paralogs/3493010/2 . We slightly altered their `Rscript.R` to simplify file paths and specify one missing variable. This modified script and their data files are available in the github repository for this paper, as are the intermediate files that were generated by their analysis script that we used in our own analyses. We obtained the `Compara.75.protein.nh.emf` gene trees [@Herrero:2016jj] from ftp://ftp.ensembl.org/pub/release-75/emf/ensembl-compara/homologies/ and include them in our github repository. These gene trees include branch lengths, annotate each internal node as being a duplication or speciation event, and provide a clade label for each internal node.

@@

	g_k_density = 
		ggplot(D, aes(x,y)) + 
			geom_line() + 
			geom_polygon( data = shade, aes(x, y) ) +
			xlab("K") +
			ylab("density") +
			theme_classic() +
			geom_vline(xintercept = thresh, col="grey") +
			geom_text(aes(x=thresh, label=thresh_label, y=mean(range(y))), colour="grey", angle=90) +
			ggtitle( "" )
